Reproducing Results in Snowden G-Comp Paper

### 2019-07-16 g_comp_example_snowden.Rmd
update

Using code from Snowden paper to try out MSM models and maybe test out SuperLearner and Target Maximum Likelihood packages.

```{r libraries, message=F}
library(tidyverse)
library(broom)
library(SuperLearner)
library(tmle)
```

@@

```{r gcomp boot}
# percentile method with broom
set.seed(321)
boot_msm <- simdata %>% bootstrap(1000) %>% 
  do(tidy(g_comp_func(data = ., y = "Y", a = "A", q_mod = "A+W1+A:W2",
            mod_family = "gaussian", estimate = "diff")))

@@

# fill matrix 
estimates[,1] <- round(gcomp_est,3)
estimates[,2] <- round(quantile(boot_msm$x, 0.5),3)
estimates[,3] <- round(quantile(boot_msm$x, 0.025),3)
estimates[,4] <- round(quantile(boot_msm$x, 0.975),3)

@@

```{r iptw boot}
# percentile method with broom
set.seed(321)
boot_iptw <- simdata %>% bootstrap(1000) %>% 
  do(tidy(iptw_func(data=., y="Y", a="A", w="W1+W2", estimate="diff")))

@@

# fill matrix 
estimates[,1] <- round(iptw_est,3)
estimates[,2] <- round(quantile(boot_iptw$x, 0.5),3)
estimates[,3] <- round(quantile(boot_iptw$x, 0.025),3)
estimates[,4] <- round(quantile(boot_iptw$x, 0.975),3)

@@

```{r tmle q mod, message=F}
# register superlearner library
sl_lib <- c("SL.glm", "SL.glm.interaction", "SL.gam", "SL.nnet", 
            "SL.randomForest", "SL.step")

@@

head(cbind(simdata, expected_y_obsexp, expected_y_a1, expected_y_a0))

@@

```{r tmle package}
set.seed(123)
tmle_package_result <- tmle(Y = simdata$Y, A = simdata$A, 
  W = subset(simdata, select = -c(A,Y)),
  Q.SL.library = c("SL.nnet", "SL.glm", "SL.randomForest", "SL.step",
        "SL.glm.interaction"), 
  g.SL.library = c("SL.nnet", "SL.glm", "SL.randomForest", "SL.step",
        "SL.glm.interaction"),  V = 10)

tmle_package_result
```

Wow. This was much faster and produced 95% CIs. TMLE has it's own formla for calculating SE as described in package description in J of Stats Software. It tells me the same thing as the MSM bootstrapped method.

>>>>

Using code from Snowden paper to try out MSM models and SuperLearner and Target Maximum Likelihood packages.

```{r libraries, message=F}
library(tidyverse)
library(rsample)
library(SuperLearner)
library(tmle)
```

@@

```{r gcomp boot}
# set funciton to handle splits for rsample package
simple_sub <- function(split){
  MSModelR::g.formula(data = analysis(split), y = "Y", a = "A", 
                      q.model = "A+W1+A:W2", 
                      model.family = "gaussian", estimate = "diff")
}

# percentile method with broom
set.seed(321)
boot_msm <- simdata %>% 
  bootstraps(times = 1000) %>% 
  mutate(coef = map(splits, simple_sub)) %>% 
  unnest(coef)

@@

# fill matrix 
estimates[,1] <- round(gcomp_est,3)
estimates[,2] <- round(quantile(boot_msm$coef, 0.5),3)
estimates[,3] <- round(quantile(boot_msm$coef, 0.025),3)
estimates[,4] <- round(quantile(boot_msm$coef, 0.975),3)

@@

```{r iptw boot}
# percentile method with rsample
set.seed(321)

iptw <- function(split){
  iptw_func(data = analysis(split), 
                 y="Y",a="A",w="W1+W2",estimate="diff")
  }

boot_iptw <- simdata %>% 
  bootstraps(times = 1000) %>% 
  mutate(coef = map(splits, iptw)) %>% 
  unnest(coef)

@@

# fill matrix 
estimates[,1] <- round(iptw_est,3)
estimates[,2] <- round(quantile(boot_iptw$coef, 0.5),3)
estimates[,3] <- round(quantile(boot_iptw$coef, 0.025),3)
estimates[,4] <- round(quantile(boot_iptw$coef, 0.975),3)

@@

```{r tmle q mod, message=F}
# register superlearner library
sl_lib <- c("SL.glm", "SL.glm.interaction", "SL.gam", "SL.glmnet","SL.step")

@@

head(cbind(simdata, expected_y_obsexp, expected_y_a1, expected_y_a0))
```

@@

```{r tmle package}
set.seed(123)
tmle_package_result <- tmle(Y = simdata$Y, A = simdata$A, 
  W = subset(simdata, select = -c(A,Y)),
  Q.SL.library = c("SL.glm", "SL.step",
        "SL.glm.interaction", "SL.xgboost"), 
  g.SL.library = c("SL.glm", "SL.step",
        "SL.glm.interaction", "SL.xgboost"),  V = 10)

summary(tmle_package_result)
```

This was much faster and produced 95% CIs. TMLE has it's own formla for calculating SE as described in package description in J of Stats Software. It tells me the same thing as the MSM bootstrapped method.
